Light Transport Techniques for Tensor Field Visualization

### 2019-07-31 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Tensor Fields - Tensor Field Lines}}

\begin{columns}
\begin{column}{.6\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Procedure}}
follow major/minor eigenvectors along pathlines
\end{block}
\end{small}
\bigskip
\begin{small}
\begin{itemize}
	\item ambiguity for nearly isotropic cases:\\ small changes in components effect large changes in tensor field line orientation (see Fig.)
	\item therefore susceptive to noise in data
	\item trajectories can cross each other\\
	$\Rightarrow$ effects erroneous trajectories, hard to interpret
\end{itemize}
\end{small}

\end{column}
\begin{column}{.4\textwidth}
\centering
\begin{figure}[t]
\centering
\includegraphics[height=0.8\textwidth]{nearly_isotropic.pdf}
\caption*{Ambiguity}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

>>>>

\frame{
\frametitle{{Random Test Field}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{itemize}
	\item numerics: limit number representation to a particular range
	\bigskip
	\item characteristic ellipsoid area: $A=\sigma_1\cdot\sigma_2\cdot\pi$
	$\Rightarrow$ preposition for high tensor magnitudes: $\sigma_1\approx\sigma_2\approx1.0$ (implicit spherical isotropy)\bigskip
	\item local normalization is verified to emphasize regions with increased anisotropy
\end{itemize}
\end{small}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[!t]
\centering
    \includegraphics[width=0.33\textwidth]{random-global.png} a)
    \includegraphics[width=0.33\textwidth]{random-local.png} b)
    \includegraphics[width=0.33\textwidth]{random_global.png} c)
    \includegraphics[width=0.33\textwidth]{random_local_slice0.png}	d)
    \caption*{Random test field : a) Glyphs, b) Local normalization, c) Tensor magnitude d) LTG}
\label{bow_contour}
\end{figure}
%\begin{figure}[!t]
%\centering
%    
%    
%\label{bow_contour}
%\end{figure}
\end{column}
\end{columns}

} % END OF FRAME
